MLH1 data report 

### 2017-11-02 rmd_report.rmd
some updates to Rmd, removed fake CAST female

```{r}

@@

#Add fake CAST female data
last_row <-data.frame(Batch = c("100", "100"), X= c("",""), Original.Name=c("12dec18_20dec20_CAST_f1_sp1_12_1_rev.tif", "12dec18_20dec20_CAST_f1_sp1_12_2_rev.tif"), Random.Name = c("1234567.tif","123456789.tif"), quality=c(1,1),nMLH1.foci =c(25,22), XY.paired =c("no","no"), REDO.crop =c("no","no"),n =c(20,20), achiasmate=c(0,0),asynased=c(0,0),notes=c("",""),category = c("CAST female","CAST female"), strain= c("CAST","CAST"), sex=c("female","female"),adj_nMLH1.foci=c(25,22),mouse=c("20dec20_CAST_f1","20dec20_CAST_f1") )

MLH1_data <- rbind(MLH1_data, last_row)

@@

```{r first boxplots, echo=FALSE, fig.align='center'}
#the below ordering works!! keep it
MLH1_data$strain<- factor(MLH1_data$strain, levels =c("G", "LEWES",
                              "WSB", "PWD","MSM","CAST", "HIM", "SPRET"), order=T )
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])
#set the order of another column, based on another variable (so that when)

@@

ff <- ggplot(MLH1_data, aes(x = as.factor(mouse), y = adj_nMLH1.foci, fill= strain )) + geom_boxplot()  + ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00", "yellowgreen", "green", "grey" ))
ff <- ff   + facet_wrap(~ sex, scales="free")
ff

#

@@

qq <- ggplot(highest_qual_df, aes(x = mouse, y = adj_nMLH1.foci)) + geom_boxplot(data = highest_qual_df, aes(fill = factor(strain) ) ) +  ggtitle("Cells with quality scores of 2 or 1") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",
  "coral1", "#E69F00", "yellowgreen","black", "grey"  ))
high_qual_boxplot <- qq + facet_wrap(~ sex, scales="free") #this is breaking the kniting... 
```

>>>>

```{r,echo=FALSE}

@@

@@

```{r first boxplots, echo=FALSE, fig.align='center'}
#the below ordering works!! keep it
MLH1_data$strain<- factor(MLH1_data$strain, levels =c("G", "LEWES",
                              "WSB", "PWD","MSM","CAST","HMI","SPRET", "other"), order=T )
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])
#set the order of another column, based on another variable (so that when)

@@

ff <- ggplot(MLH1_data, aes(x = as.factor(mouse), y = adj_nMLH1.foci, fill= strain )) + geom_boxplot()  + ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00", "yellowgreen", "green", "grey" ))
ff <- ff   + facet_wrap(~ sex, scales="free")

#boxplots by strain
ss <- ggplot(MLH1_data, aes(x = as.factor(strain), y = adj_nMLH1.foci, fill= strain )) + geom_boxplot()  + ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00", "yellowgreen", "green", "grey" ))
ss <- ss   + facet_wrap(~ sex, scales="free")

ff
ss
```

@@

qq <- ggplot(highest_qual_df, aes(x = mouse, y = adj_nMLH1.foci)) + geom_boxplot(data = highest_qual_df, aes(fill = factor(strain) ) ) +  ggtitle("Cells with quality scores of 2 or 1") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00", "yellowgreen", "green", "grey" ))
high_qual_boxplot <- qq + facet_wrap(~ sex, scales="free") #this is breaking the kniting... 
```
